formula1_start_vs_finish.Rmd

### 2024-04-12 inst/formula1_start_vs_finish.Rmd
typo

```{r max_alpha,cache=TRUE}
system.time(alpha_MLE <- optimize(function(a){f(a,topn=topn,finish=finish,grid=grid)[1]},c(0.95,0.99),maximum=TRUE))
alpha_MLE
```

>>>>

```{r max_alpha,cache=TRUE}
system.time(alpha_MLE <- optimize(function(a){f(a,topn=topn,finish=finish,grid=grid)[1]},c(0.90,0.95),maximum=TRUE))
alpha_MLE
```
